Methodology

Method 1: Spectrogram 

#####  Main idea: Editing the fft.R source package of av package to achieve the log transformation of y-axis (frequency), and remove the 0 value of y-axis, and re-run the local av package.



##### install the modified version of av package from local
install.packages("/path/av", repos = NULL, type="source")

Calculate the frequency data and plot the spectrogram:

```{r plot_spectrogram}
library(av)
library(tuneR)
chip_song <- "Super_Mario.mp3"
song <- chip_song
# Read first 10 sec of song
pcm_data <- read_audio_bin(song, end_time = 10.0)
plot(pcm_data, type = 'l')

# Read 10 sec of data and make fft
fft_data <- read_audio_fft(song, end_time = 10.0)

frequency_values <- attr(fft_data, 'frequency')
summary(frequency_values)
dim(fft_data)

# Plot the spectrogram
plot(fft_data, ovlp = 0.6, window = hanning(1024))
```

Turn off dark mode to use the default R colors:

```{r default color}
plot(fft_data, dark = FALSE, ovlp = 0.6, window = hanning(1024))
```

### Spectrogram video

Create a spectrogram video:

```{r spectrogram_video}
# Create new audio file with first 10 sec
av_audio_convert(song, 'short.mp3', total_time = 10.0)
av_spectrogram_video('short.mp3', output = 'spectrogram.mp4', width = 1280, height = 720, res = 144)
```

### Compare with seewave

Compare spectrograms with the seewave package:

```{r}
library(tuneR)
song <- readMP3("Super_Mario.mp3")
print(song)
```

For mono channels:

```{r seewave_mono}
library(seewave)
library(ggplot2)

# Extract the mono channel
song_mono <- mono(song)

# Generating the spectrogram:
ggspectro(song_mono, ovlp = 0.01, window = hanning(1024)) + 
  geom_tile(aes(fill = amplitude)) + 
  stat_contour() + 
  coord_cartesian(xlim = c(0, 10)) # Generates spectrogram for first 10 seconds only
```

For comparing stereo channel side by side:

```{r stereo_left}
# exract the left channel of the stereo type and make FFT
audio_left <- song@left
left_wave <- Wave(audio_left, samp.rate = song@samp.rate, bit = song@bit)

ggspectro(left_wave, ovlp = 0.01, window = hanning(1024)) + 
  geom_tile(aes(fill = amplitude)) + 
  stat_contour() + 
  coord_cartesian(xlim = c(0, 10)) # Generates spectrogram for first 10 seconds only
```

```{r stereo_right}
# exract the right channel of the stereo type and make FFT
audio_right <- audio@right
right_channel <- Wave(audio_right, samp.rate = song@samp.rate, bit = song@bit)

ggspectro(right_channel, ovlp = 0.01, window = hanning(512)) + 
  geom_tile(aes(fill = amplitude)) + 
  stat_contour() + 
  coord_cartesian(xlim = c(0, 10)) # Generates spectrogram for first 10 seconds only
```

### For av package:

```{r av_mono}
song_mono <- mono(song)
savewav(song_mono, f = song@samp.rate, filename = 'seewave_mono.wav')

# Read 10 sec of data and make fft
fft_data_mono <- read_audio_fft('seewave_mono.wav', end_time = 10.0)
plot(fft_data_mono, ovlp = 0.6, window = hanning(1024))
```

```{r av_left}
audio_left <- song@left
song_left <- Wave(audio_left, samp.rate = song@samp.rate, bit = song@bit)
savewav(song_left, filename = 'seewave_left.wav')

# Read 10 sec of data and make fft
fft_data_left <- read_audio_fft('seewave_left.wav', end_time = 10.0)
plot(fft_data_left, ovlp = 0.6, window = hanning(1024))
```

```{r av_right}
audio_right <- song@right
song_right <- Wave(audio_right, samp.rate = song@samp.rate, bit = song@bit)
savewav(song_right, filename = 'seewave_right.wav')

# Read 10 sec of data and directly transform to frequency
fft_data_right <- read_audio_fft('seewave_right.wav', end_time = 10.0)
plot(fft_data_right, ovlp = 0.6, window = hanning(1024))
```
